---
title: "Attractive LLIN"
author: "Nicolas Moiroux"
date: "15 March 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(citr)
library(tidyverse)
library(pse)
library(ggpubr)
library(ggbeeswarm)
source("R/Fun_VLAIB_fRTP.R")
source("R/Fun_fitness_f_kdr.R")
source("R/Fun_predict_kdr.R")
insertSource("R/my_ggarrange.R", package = "ggpubr")

```

## Results
```{r echo=FALSE}
# determine reference value of preference for deterrent LLIN (mean of pref among ITN that were significantly deterrent in Moiroux et al. 2017)
Data_deterence <- read.delim("data/Data_Figures2_Moiroux.txt")
Data_deterence %>% 
	filter(IC_high < 1) %>%	       # select only significantly deterent ITNs
	mutate(pLLIN=RR/(RR+1)) %>%    # convert Rate-ratio to preference values
	summarise(mean= mean(pLLIN)) %>%
	round(2)-> pLLIN_ref_det	 # compute the mean preference value
```

We simulated the effect of providing human communities with attractive LLINs on malaria transmission in comparison with communities receiving inert or deterrent LLINs. Attractive LLINs used in these simulation induced vector preferences (parameter pLLIN, Table 1) of 0.6 and 0.7: a vector preference for LLINs of 0.6 indicates that 60% of malaria vectors choose a human under an LLIN if presented against an unprotected human. Vector preferences of 0.6 and 0.7 have been observed several times in nature ( and Supplementary Figure 1). The reference inert LLIN induced a vector preference for LLIN of 0.5 (i.e, no preference). Vector preference of the reference deterrent LLIN was set to `r pLLIN_ref_det` (only `r round(pLLIN_ref_det*100,0)`% of malaria vectors choose a human under an LLIN if presented against an unprotected human) that is the mean preference value among significantly deterrent ITNs in [1]. We also simulated the effect of inert LLINs against the reference deterrent LLIN.


### Effect of LLIN coverage
```{r echo=FALSE}
#### figure 1 (coverage) ----
# common value for Fig1 to 4
legend_title <- "Vector preference for LLINs"
y_title <- "% reduction in vectorial capacity"
aspect_ratio <- 2.5
height <- 7
#ggsave(g, height = 7 , width = 7 * aspect_ratio)
# common parameters
cov <- seq(0,1,by = 0.01)	  # coverage LLIN
FUN <- IC                # function used to calculate vectorial capacity
# panel A
p<- c(0.6,0.7)		      # preference for LLIN protected human (against unprotected human) 
ref_pref <- 0.5							# preference value of the reference LLIN (inert = 0.5)


RTP.fit <- expand.grid(p.=p,cov.=cov)   # create table of all combinations of p and cov
RTP.fit <- mutate(RTP.fit, z = pmap_dbl(list(cov.,p.),~fRTP(p=.y, Uh=.x, Uh2=.x, p2=ref_pref,FUN= FUN))) # calculate VC ratio
RTP.fit$redVC <- -(1-RTP.fit$z)*100        # reduction in VC

fig1_A <- ggplot(RTP.fit, aes(x=cov.*100, y=redVC)) + 
	xlab("LLIN Coverage (%)") + 
	geom_line(aes(linetype=as.factor(p.))) +
	scale_linetype_manual(values=c(2,3),name=legend_title)+
	xlim(0,100) + ylim(-100,0)+
	theme(aspect.ratio=1) +
	theme(axis.title.y = element_blank())+
	theme(axis.title.x = element_blank())

# panel B
p<- c(0.5,0.6,0.7)		      # preference for LLIN protected human (against unprotected human) 
ref_pref <- 0.36							# preference value of the reference LLIN (attractive = 0.3)

RTP.fit <- expand.grid(p.=p,cov.=cov)   # create table of all combinations of p and cov
RTP.fit <- mutate(RTP.fit, z = pmap_dbl(list(cov.,p.),~fRTP(p=.y, Uh=.x, Uh2=.x, p2=ref_pref,FUN= FUN))) # calculate VC ratio
RTP.fit$redVC <- -(1-RTP.fit$z)*100        # reduction in VC

fig1_B <- ggplot(RTP.fit, aes(x=cov.*100, y=redVC)) + 
	xlab("LLIN Coverage (%)") + 
	geom_line(aes(linetype=as.factor(p.))) +
	scale_linetype_manual(values=c(1,2,3),name=legend_title)+
	xlim(0,100) + ylim(-100,0)+
	theme(aspect.ratio=1) +
	theme(axis.title.y = element_blank())+
	theme(axis.title.x = element_blank())


# arrange panels of figure 1
figure1 <- ggarrange(fig1_A + rremove("legend"), 
										 fig1_B + rremove("legend"), 
										 common.legend = TRUE,
										 plot_legend = 2,
										 labels = c("A", "B"),
										 ncol = 2, nrow = 1)

figure1 <- annotate_figure(figure1,
								bottom = text_grob("LLIN coverage (%)"),
								left = text_grob(y_title, rot=90))

## search coverage value for which reduction in transmission is the higher
fig1_A$data %>% group_by(p.) %>% summarise(min=min(redVC)) -> minVC
fig1_A$data %>% filter(redVC %in% minVC$min) -> fig1A_min

fig1_B$data %>% group_by(p.) %>% summarise(min=min(redVC)) -> minVC
fig1_B$data %>% filter(redVC %in% minVC$min) -> fig1B_min

rg_minVC <- unique(c(fig1A_min$cov,fig1B_min$cov ))
lo_rg_minVC <- min(rg_minVC)*100
hi_rg_minVC <- max(rg_minVC)*100
```

According to our model, attractive LLINs are expected to reduce malaria transmission in comparison to inert or deterrent LLINs whatever the coverage percentage. When all other parameters of the model were set at default values (Table 1), the maximum reduction was reached at `r lo_rg_minVC`-`r hi_rg_minVC` % coverage. At these coverage rates, an highly attractive LLIN (pLLIN= 0.7) is expected to reduce malaria transmission (expressed as vectorial capacity) by `r -round(fig1A_min[2,4],2)` % compared to an inert LLIN (Figure 1A) and by `r -round(fig1B_min[3,4],2)` % compared to a deterrent one (Figure 1B). At `r lo_rg_minVC`-`r hi_rg_minVC` % coverage, slightly attractive LLINs (pLLIN= 0.6) are expected to reduce malaria transmission by `r -round(fig1A_min[1,4],2)` and `r -round(fig1B_min[2,4],2)` % when compared to inert and deterrent LLINs, respectively (Figure 1A and 1B). 

```{r, echo=FALSE, fig.height = 3.5, fig.width = 6, fig.align = "center"}
figure1
```

##### Figure 1: Reduction of malaria transmission induced (A) by attractive Long-lasting Insecticidal Nets (LLINs) compared to inert ones and (B) by attractive and inert LLIN compared to deterrent ones for varied levels of LLIN coverage in the human population.
###### *An attraction rate of 0.6 indicates that 60% of malaria vectors choose a human under an LLIN if presented against an unprotected human. The reference inert LLIN (panel A) has an attraction rate of 0.5 (no preference between LLIN protected or unprotected humans) and the reference deterrent LLIN (panel B) has an attraction rate of 0.36 (only 36% of the vectors choose an LLIN protected human against an unprotected human).*

### Effect of physiological and behavioral resistance
```{r echo=FALSE}
m <- seq(0,1,by = 0.01)	  # pre-bite mortality

# panel A
p<- c(0.6,0.7)		      # preference for LLIN protected human (against unprotected human) 
ref_pref <- 0.5							# preference value of the reference LLIN (inert = 0.5)


RTP.fit <- expand.grid(p.=p,m.=m)   # create table of all combinations of p and m
RTP.fit <- mutate(RTP.fit, z = pmap_dbl(list(m.,p.),~fRTP(p=.y, m=.x, m2=.x, p2=ref_pref,FUN= FUN))) # calculate VC ratio
RTP.fit$redVC <- -(1-RTP.fit$z)*100        # reduction in VC

fig2_A <- ggplot(RTP.fit, aes(x=(1-m.)*100, y=redVC)) + 
	xlab("Feeding attempt survival (%)") + 
	geom_line(aes(linetype=as.factor(p.))) +
	scale_linetype_manual(values=c(2,3),name=legend_title)+
	xlim(0,100) + ylim(-100,0)+
	theme(aspect.ratio=1) +
	theme(axis.title.y = element_blank())+
	theme(axis.title.x = element_blank())

# panel B
p<- c(0.5,0.6,0.7)		      # preference for LLIN protected human (against unprotected human) 
ref_pref <- 0.36							# preference value of the reference LLIN (inert = 0.5)

RTP.fit <- expand.grid(p.=p,m.=m)   # create table of all combinations of p and m
RTP.fit <- mutate(RTP.fit, z = pmap_dbl(list(m.,p.),~fRTP(p=.y, m=.x, m2=.x, p2=ref_pref,FUN= FUN))) # calculate VC ratio
RTP.fit$redVC <- -(1-RTP.fit$z)*100        # reduction in VC

fig2_B <- ggplot(RTP.fit, aes(x=(1-m.)*100, y=redVC)) + 
	xlab("feeding attempt survival (%)") + 
	geom_line(aes(linetype=as.factor(p.))) +
	scale_linetype_manual(values=c(1,2,3),name=legend_title)+
	xlim(0,100) + ylim(-100,0)+
	theme(aspect.ratio=1) +
	theme(axis.title.y = element_blank())+
	theme(axis.title.x = element_blank())


# arrange panels of figure 1
figure2 <- ggarrange(fig2_A + rremove("legend"), 
										 fig2_B + rremove("legend"), 
										 common.legend = TRUE,
										 plot_legend = 2,
										 labels = c("A", "B"),
										 ncol = 2, nrow = 1)

figure2 <- annotate_figure(figure2,
								bottom = text_grob("Feeding attempt survival (%)"),
								left = text_grob(y_title, rot=90))

## search reduction in transmission value for survival set to 0 (no resistance)
fig2_A$data %>% filter(m. == 1) -> fig2A_lo
fig2_B$data %>% filter(m. == 1) -> fig2B_lo
## search reduction in transmission value for survival set to 1 (max resistance)
fig2_A$data %>% filter(m. == 0) -> fig2A_hi
fig2_B$data %>% filter(m. == 0) -> fig2B_hi
```

We simulated the effect of attractive LLIN in various scenario of physiological and behavioral insecticide resistance in vectors. Here, we define physiological resistance as the ability to survive feeding attempt in a dwelling equipped with an LLIN. In our model, the probability to survive a feeding attempt equals the probability to successfully take a blood-meal (conditioned on not being diverted; Figure 6). Our simulations show that whatever the level of physiological resistance in the vector population, attractive LLINs are always most efficient than inert or deterrent LLINs (Figure 2A and 2B) but the reduction in transmission lowered as resistance increased. In the absence of physiological resistance (i.e. 0% survival), all other parameters being equals (Table 1), we can expect to reduce malaria transmission by `r -round(fig2A_lo[1,4],2)`% and `r -round(fig2A_lo[2,4],2)`% with moderately (pLLIN=0.6) and highly attractive (pLLIN=0.7) LLINs, respectively, when compared to an inert LLIN (Figure 2A). When compared to a deterrent LLIN in the same conditions (no resistance), an inert LLIN is exepcted to reduce malaria transmission by `r -round(fig2B_lo[1,4],2)`% while moderately (pLLIN=0.6) and highly attractive (pLLIN=0.7) are expected to reduce malaria transmissiion by `r -round(fig2B_lo[2,4],2)`% and `r -round(fig2B_lo[3,4],2)`%, respectively. When resistance is maximal, attractive LLINs provide a better community protection but with moderate reduction of transmission ranging from `r -round(fig2A_hi[1,4],2)`% to `r -round(fig2A_hi[2,4],2)`% (Figure 2A) against inert LLINs and from `r -round(fig2B_hi[2,4],2)`% to `r -round(fig2B_hi[3,4],2)`% against deterrent LLINs (Figure 2B). 

```{r, echo=FALSE, fig.height = 3.5, fig.width = 6, fig.align = "center"}
figure2
```

##### Figure 2: Reduction of malaria transmission induced (A) by attractive Long-lasting Insecticidal Nets (LLINs) compared to inert ones and (B) by attractive and inert LLIN compared to deterrent ones for varied levels of physiological resistance in the vector population.
###### *An attraction rate of 0.6 indicates that 60% of malaria vectors choose a human under an LLIN if presented against an unprotected human. The reference inert LLIN (panel A) has an attraction rate of 0.5 (no preference between LLIN protected or unprotected humans) and the reference deterrent LLIN (panel B) has an attraction rate of 0.36 (only 36% of the vectors choose an LLIN protected human against an unprotected human).*

```{r, echo=FALSE}
d <- seq(0,1,by = 0.01)	  # diversion probability
# panel A
p<- c(0.6,0.7)		        # preference for LLIN protected human (against unprotected human) 
ref_pref <- 0.5							# preference value of the reference LLIN (inert = 0.5)

RTP.fit <- expand.grid(p.=p,d.=d)   # create table of all combinations of p and d
RTP.fit <- mutate(RTP.fit, z = pmap_dbl(list(d.,p.),~fRTP(p=.y, D=.x, D2=.x, p2=ref_pref,FUN= FUN))) # calculate VC ratio
RTP.fit$redVC <- -(1-RTP.fit$z)*100        # reduction in VC

fig3_A <- ggplot(RTP.fit, aes(x=d.*100, y=redVC)) + 
	xlab("Escaping (%)") + 
	geom_line(aes(linetype=as.factor(p.))) +
	scale_linetype_manual(values=c(2,3),name=legend_title)+
	xlim(0,100) + ylim(-100,0)+
	theme(aspect.ratio=1) +
	theme(axis.title.y = element_blank())+
	theme(axis.title.x = element_blank())

# panel B
p<- c(0.5,0.6,0.7)		      # preference for LLIN protected human (against unprotected human) 
ref_pref <- 0.36							# preference value of the reference LLIN (inert = 0.5)

RTP.fit <- expand.grid(p.=p,d.=d)   # create table of all combinations of p and d
RTP.fit <- mutate(RTP.fit, z = pmap_dbl(list(d.,p.),~fRTP(p=.y, D=.x, D2=.x, p2=ref_pref,FUN= FUN))) # calculate VC ratio
RTP.fit$redVC <- -(1-RTP.fit$z)*100        # reduction in VC

fig3_B <- ggplot(RTP.fit, aes(x=d.*100, y=redVC)) + 
	xlab("Escaping (%)") + 
	geom_line(aes(linetype=as.factor(p.))) +
	scale_linetype_manual(values=c(1,2,3),name=legend_title)+
	xlim(0,100) + ylim(-100,0)+
	theme(aspect.ratio=1) +
	theme(axis.title.y = element_blank())+
	theme(axis.title.x = element_blank())


# arrange panels of figure 1
figure3 <- ggarrange(fig3_A + rremove("legend"), 
										 fig3_B + rremove("legend"), 
										 common.legend = TRUE,
										 plot_legend = 2,
										 labels = c("A", "B"),
										 ncol = 2, nrow = 1)

figure3 <- annotate_figure(figure3,
								bottom = text_grob("Escaping (%)"),
								left = text_grob(y_title, rot=90))

## search reduction in transmission value for escaping set to 0 (no quantitative bahavioral resistance)
fig3_A$data %>% filter(d. == 0) -> fig3A_lo
fig3_B$data %>% filter(d. == 0) -> fig3B_lo
## search reduction in transmission value for escaping set to 1 (max quantitative bahavioral resistance)
fig3_A$data %>% filter(d. == 1) -> fig3A_hi
fig3_B$data %>% filter(d. == 1) -> fig3B_hi
```


Then, we analyzed the effect of behavioral resistances on the efficacy of attractive LLINs. We simulated an increasing level of indoor escaping by varying the value of the diversion probability D_p in our model (Figure X). A diverted mosquito postpones host-seeking to next night. The simulations showed that whatever the level of indoor escaping, attractive LLIN are always better than inert and attractive ones to reduce malaria transmission. As indoor escaping increased, the relative efficacy of attractive LLINs decreased. When compared to an inert LLIN, a moderately attractive LLIN is expected to reduce malaria transmission by `r -round(fig3A_hi[1,4],2)`% (high resistance, 100% escaping) to `r -round(fig3A_lo[1,4],2)`(lo) % (no resistance, 0% escaping) while a highly attractive LLIN is expected to reduce malaria transmission by `r -round(fig3A_hi[2,4],2)`% (high resistance, 100% escaping) to `r -round(fig3A_lo[2,4],2)`% (no resistance, 0% escaping) (Figure 3A). When compared to a deterrent LLIN with high resistance (100% escaping), inert and attractive LLINs are expected to reduce malaria transmission by `r -round(fig3B_hi[1,4],2)`-`r -round(fig3B_hi[3,4],2)` % and by `r -round(fig3B_lo[1,4],2)`-`r -round(fig3B_hi[3,4],2)`%, respectively, in absence of resistance (0% escaping; Figure 3B).

```{r, echo=FALSE, fig.height = 3.5, fig.width = 6, fig.align = "center"}
figure3
```

##### Figure 3: Reduction of malaria transmission induced (A) by attractive Long-lasting Insecticidal Nets (LLINs) compared to inert ones and (B) by attractive and inert LLIN compared to deterrent ones for varied levels of quantitative behavioral resistance (escaping) in the vector population.
###### *An attraction rate of 0.6 indicates that 60% of malaria vectors choose a human under an LLIN if presented against an unprotected human. The reference inert LLIN (panel A) has an attraction rate of 0.5 (no preference between LLIN protected or unprotected humans) and the reference deterrent LLIN (panel B) has an attraction rate of 0.36 (only 36% of the vectors choose an LLIN protected human against an unprotected human).*


```{r, echo=FALSE}
pi <- seq(0,1,by = 0.01)	  # proportion of exposure to bite during which LLIN is in use
# panel A
p<- c(0.6,0.7)		        # preference for LLIN protected human (against unprotected human) 
ref_pref <- 0.5							# preference value of the reference LLIN (inert = 0.5)

RTP.fit <- expand.grid(p.=p,pi.=pi)   # create table of all combinations of p and pi
RTP.fit <- mutate(RTP.fit, z = pmap_dbl(list(pi.,p.),~fRTP(p=.y, pi=.x, pi2=.x, p2=ref_pref,FUN= FUN))) # calculate VC ratio
RTP.fit$redVC <- -(1-RTP.fit$z)*100        # reduction in VC

fig4_A <- ggplot(RTP.fit, aes(x=(1-pi.)*100, y=redVC)) + 
	xlab("Spatial-temporal avoidance (%)") + 
	geom_line(aes(linetype=as.factor(p.))) +
	scale_linetype_manual(values=c(2,3),name=legend_title)+
	xlim(0,100) + ylim(-100,0)+
	theme(aspect.ratio=1) +
	theme(axis.title.y = element_blank())+
	theme(axis.title.x = element_blank())

# panel B
p<- c(0.5,0.6,0.7)		      # preference for LLIN protected human (against unprotected human) 
pi <- seq(0,1,by = 0.01)	  # 
ref_pref <- 0.36							# preference value of the reference LLIN (inert = 0.5)
FUN <- IC                # function used to calculate vectorial capacity

RTP.fit <- expand.grid(p.=p,pi.=pi)   # create table of all combinations of p and d
RTP.fit <- mutate(RTP.fit, z = pmap_dbl(list(pi.,p.),~fRTP(p=.y, pi=.x, pi2=.x, p2=ref_pref,FUN= FUN))) # calculate VC ratio
RTP.fit$redVC <- -(1-RTP.fit$z)*100        # reduction in VC

fig4_B <- ggplot(RTP.fit, aes(x=(1-pi.)*100, y=redVC)) + 
	xlab("Spatial-temporal avoidance (%)") + 
	geom_line(aes(linetype=as.factor(p.))) +
	scale_linetype_manual(values=c(1,2,3),name=legend_title)+
	xlim(0,100) + ylim(-100,0)+
	theme(aspect.ratio=1) +
	theme(axis.title.y = element_blank())+
	theme(axis.title.x = element_blank())


# arrange panels of figure 4
figure4 <- ggarrange(fig4_A + rremove("legend"), 
										 fig4_B + rremove("legend"), 
										 common.legend = TRUE,
										 plot_legend = 2,
										 labels = c("A", "B"),
										 ncol = 2, nrow = 1)

figure4 <- annotate_figure(figure4,
								bottom = text_grob("Spatial-temporal avoidance (%)"),
								left = text_grob(y_title, rot=90))

## search reduction in transmission value for spatial-temporal avoidance set to 0 (no qualitative bahavioral resistance)
fig4_A$data %>% filter(pi. == 1) -> fig4A_lo
fig4_B$data %>% filter(pi. == 1) -> fig4B_lo
## search reduction in transmission value for spatial-temporal avoidance set to 0.5 (50 % of exposure to bite occurs when LLIN are not in use)
fig4_A$data %>% filter(pi. == 0.5) -> fig4A_mi
fig4_B$data %>% filter(pi. == 0.5) -> fig4B_mi

```


Mosquito vectors of malaria are able to change their behavior to be active for blood searching in spaces and at times when and where people are not using LLINs [refs]. We simulated this spatial-temporal avoidance of LLIN by varying parameter Π that is the proportion of human exposure to bite that occurs while LLINs are in use, or in other terms, the proportion of total bites prevented by using an LLIN. When spatial-temporal avoidance increases, Π decreases. Whatever the rate of spatial-temporal avoidance, attractive LLIN allowed to reduce malaria transmission compared to inert (Figure 4A) and deterrent (Figure 4B) LLINs. As spatial-temporal avoidance increases, the benefit of using attractive LLIN decreases. By 50% of spatial-temporal avoidance, attractive LLINs are expected to reduce malaria transmission by `r -round(fig4A_mi[1,4],2)`-`r -round(fig4A_mi[2,4],2)`% when compared to inert LLINs and by `r -round(fig4B_mi[2,4],2)`-`r -round(fig4B_mi[3,4],2)`% compared to deterrent LLINs. When compared to a deterent LLIN with 50% of spatial-temporal avoidance, an inert LLIN is expected to reduce malaria transmission by `r -round(fig4B_mi[1,4],2)`%.

```{r, echo=FALSE, fig.height = 3.5, fig.width = 6, fig.align = "center"}
figure4
```

##### Figure 4: Reduction of malaria transmission induced (A) by attractive Long-lasting Insecticidal Nets (LLINs) compared to inert ones and (B) by attractive and inert LLIN compared to deterrent ones for varied levels of qualitative behavioral resistance (spatial-temporal avoidance) in the vector population.
###### *An attraction rate of 0.6 indicates that 60% of malaria vectors choose a human under an LLIN if presented against an unprotected human. The reference inert LLIN (panel A) has an attraction rate of 0.5 (no preference between LLIN protected or unprotected humans) and the reference deterrent LLIN (panel B) has an attraction rate of 0.36 (only 36% of the vectors choose an LLIN protected human against an unprotected human).*


```{r, echo=FALSE}
#### define range (min and max) values for each parameters ----
### from litterature
S_rg   <- list(min=0.61, max=0.98) # Silver 2008, Chapter 13
g_rg   <- list(min=2, max=6)			 # Afrane et al. 2005, JME; Carnevale & Robert 2009
k_rg   <- list(min=0.02, max=0.2)  # Churcher et al. 2015, Nat. Comm
n_rg   <- list(min=8, max=16)			 # Hien 2016, Plos Path; Ohm et al. 2018, Par.& Vec.
Uh_rg  <- list(min=0.1, max=0.9)	 # Malaria Atlas Project 
Ih_rg  <- list(min=0.1, max=0.9)   # Malaria Atlas Project 
pi_rg  <- list(min=0.45, max=1)    # Cooke et al. 2015, Malaria Journal

### user defined
Nh_rg  <- list(min=300, max=5000)
   
### from Moiroux et al. 2017
## load summarised data of Experimental hut trials (EHT) from Moiroux et al. 2017
Data_moiroux <- read.delim("data/Data_moiroux.txt")	

Data_moiroux %>%
	dplyr::mutate(m1 = Tot_D_unfd / Total_unfd) %>% 	       # calculate pre-bite mortality
	dplyr::mutate(m2 = Tot_D_fed / Total_bfed) %>%  	       # calculate post-bite mortality
	dplyr::mutate(D = Tot_L_unfd / total) %>%   	           # calculate Diversion rate
	group_by(ITN) %>% 																			 # group by type of tretament (ITN, CTN or control)
	summarise_at(c("m1","m2","D"),funs(min,max), na.rm=TRUE) -> range_moiroux # calculate min and max values of m1, m2 and D

## find min and max values of pre-bite, post-bite mortality and diversion for untreated nets and LLINs
range_UTN <- range_moiroux %>% filter(ITN=="no") %>% select(-ITN) %>% as.data.frame()
range_ITN <- range_moiroux %>% filter(ITN=="ITN")%>% select(-ITN) %>% as.data.frame()

m1u_rg <- list(min=range_UTN[1,1], max=range_UTN[1,4])
m2u_rg <- list(min=range_UTN[1,2], max=range_UTN[1,5])
m1p_rg <- list(min=range_ITN[1,1], max=range_ITN[1,4])
m2p_rg <- list(min=range_ITN[1,2], max=range_ITN[1,5])
Du_rg  <- list(min=range_UTN[1,3], max=range_UTN[1,6])
Dp_rg  <- list(min=range_ITN[1,3], max=range_ITN[1,6])

## set preference values for the comparison of transmission
pref <- 0.6					# in the sensitivity analysis, we will compare an attractive LLIN to
pref_ref <- 0.36     # a deterrent one

#### prepare functions and data for uncertainity analysis----

### modify fRTP function to be fed with all parameters of the IC function ----
fRTP_sens <- function(nsim, S = 0.9, g = 3, Nh = 1000, Ih = 0.5, k = 0.1, n = 11, m1u = 0.05,
                                                                                  m1p = 0.72, 
                                                                                  m2u = 0.005,
                                                                                  m2p = 0.21,
																																									Du = 0.43,
                                                                                  Dp = 0.3,
                                                                                  Uh = 0.6,
                                                                                  pi = 0.9, 
                                                                                  #Pllin = 0.5,  
                                                                                  FUN = IC){
													  RTP <- FUN(nsim,S = S, g = g, Nh = Nh, Ih = Ih, k = k, n = n, 
																																			            m1u=m1u,
																																			            m1p=m1p, 
																																			            m2u=m2u,
																																			            m2p=m2p,
																																			  					Du=Du,
																																			            Dp=Dp,
																																			            Uh=Uh,
																																			            pi=pi, 
																																			            Pllin=pref)["IC"] / +
													         FUN(nsim,S = S, g = g, Nh = Nh, Ih = Ih, k = k, n = n, 
																																			        		m1u=m1u,
																																			        		m1p=m1p, 
																																			        		m2u=m2u,
																																			        		m2p=m2p,
																																			        		Du=Du,
																																			        		Dp=Dp,
																																			        		Uh=Uh,
																																			        		pi=pi, 
																																			        		Pllin=pref_ref)["IC"]
  return(-(1-RTP)*100)
}

### Uncertainty analysis following tutorial of the 'pse' package ----
## names of the parameters
factors <- c("S", "g", "Nh", "Ih", "k", "n", 
             "m1u" ,    # 0 - 0.04 (EHT Moiroux)
             "m1p",    # 0.03 - 1 (EHT Moiroux)          # TESTED
             "m2u",     # 0 - 0.01 (EHT Moiroux)
             "m2p",     # 0 - 0.5 (EHT Moiroux)
             "Du",       # 0.15 - 0.8 (EHT Moiroux)
             "Dp",     # 0 - 1                          # TESTED
             "Uh",     # 0 - 1                          # TESTED
             "pi"     # 0 - 1                          # TESTED
             #"Pllin"   # 0.1 - 0.7                      # TESTED)
             ) 


## the probability density functions for each parameter
# discrete uniform probablity function (for parameters g and n)
qdunif<-function(p, min, max) floor(qunif(p, min, max))

q <- c("qunif",  #S
       "qdunif", #g
       "qunif",  #Nh
       "qunif",  #Ih
       "qunif",  #k
       "qdunif", #n
       "qunif",  #m1u
       "qunif", #m1p     # TESTED (fixed)
       "qunif",  #m2u
       "qunif",  #m2p
       "qunif", #Du
       "qunif", #RR_fi1 # TESTED (fixed)
       "qunif", #Uh     # TESTED (fixed)
       "qunif"#, #pi     # TESTED (fixed)
       #"qunif"  #Pllin
       )


## a list containing the lists with all the parameters to the density functions ----
q.arg <- list(S_rg, #S
              g_rg, #g
              Nh_rg, #Nh
              Ih_rg,  #Ih
              k_rg, #k
              n_rg,     #n
              m1u_rg,   #m1u
              m1p_rg,  #m1p # TESTED (fixed)
              m2u_rg,   #m2u
              m2p_rg, #m2p
							Du_rg, #Du
							Dp_rg,   #Dp # TESTED (fixed)
							Uh_rg,   #Uh # TESTED (fixed)
							pi_rg#,   #pi # TESTED (fixed)
              #list(min=0.2, max=0.4)  #Pllin
              )


# function modelRun encapsulates fRTP_sens function,in a manner to receive a data.frame containing ----
# all parameter combinations and returning the results in one array.
modelRun <- function (my.data) {
  return(mapply(fRTP_sens, 100, my.data[,1], my.data[,2], my.data[,3], my.data[,4], my.data[,5], my.data[,6],
                my.data[,7], my.data[,8], my.data[,9], my.data[,10]
                , my.data[,11], my.data[,12], my.data[,13], my.data[,14]#, my.data[,15]
                ))
}

# Generates the Latin Hypercube sampling for uncertainty and sensitivity analyses.----
if(!(exists("myLHS"))){
myLHS <- pse::LHS(modelRun, factors, 500, q, q.arg, nboot=50, res.names = "% reduction in vectorial capacity")
}
# accessing the data and result data frames from an LHS object
#pse::get.data(myLHS)

# plots the empirical cumulative density function----
#pse::plotecdf(myLHS)

res_LHS <- pse::get.results(myLHS) %>%
											sort() %>%
											as.data.frame()



fig_pse_A <- res_LHS %>%
									ggplot(aes(.)) +
									stat_ecdf(geom = "step") +
									theme(axis.title.y = element_blank())
	
fig_pse_B <- res_LHS %>%
									ggplot(aes(x = "", y = .)) +
									geom_boxplot(fill = colors()[8]) +
								  geom_quasirandom(color = "darkslategrey")+
									theme(axis.title.x = element_blank())+
									coord_flip()


figure_pse <- ggarrange(fig_pse_A, 
												fig_pse_B, 
												labels = c("A", "B"),
												ncol = 1, nrow = 2,
												align="v")

figure_pse <- annotate_figure(figure_pse,
								bottom = text_grob("% reduction in vectorial capacity")#,
								#left = text_grob("value", rot=90)#,
								#fig.lab = "Figure 1", fig.lab.face = "bold"
)

# extract usefull value: median, mean and 95% credible interval
med_pred <- median(res_LHS[,1])
mean_pred <- mean(res_LHS[,1])
cred_pred <- quantile(res_LHS[,1], probs = c(0.05, 0.95))


# produces a series of scatterplots from data----
# pse::plotscatter(myLHS)

# plots the partial rank correlation coefficient from an LHS object----
# pse::plotprcc(myLHS)

# Estimates the partial inclination coefficient of a model response in relation with all model input variables----
pic <- as.data.frame(pse::pic(myLHS, nboot=40)[[1]][6])

# In order to decide whether our sample size was adequate or insufficient, we calculate
# the Symmetric Blest Measure of Agreement (SBMA) between the PRCC coefficients
# of two runs with different sample sizes.
#newLHS <- pse::LHS(modelRun, factors, 750, q, q.arg)
#(mySbma <- pse::sbma(myLHS, newLHS)) 
# 0.8986226 # It is reasonable to expect agreements around 0.7 to 0.9 in well-behaved models.

```

We performed an uncertainty and sensitivity analysis of the model to assess uncertainty of our results due to others input parameters. We therefore defined plausible ranges of values for these parameters (Table 1) and realized a Latin Hypercube Sampling (500 samples) used to run the model [Chalom 2012 arxiv]. Outputs of the models resulting from this sampling showed that attractive LLIN remains always better than inert LLINs for reducing malaria transmission (95 % credible interval of the reduction of transmission was [ , ]; figure S-X). However, our analysis indicated that the results of transmission reduction are highly sensitive to the duration of the gonotrophic cycle (Partial Inclination Coefficient PIC = `r -round(pic["g",1],2)` [`r -round(pic["g",4],2)`, `r -round(pic["g",5],2)`]) of the vectors and to the parasite extrinsic incubation period (PIC = `r -round(pic["n",1],2)` [`r -round(pic["n",4],2)`, `r -round(pic["n",5],2)`]) (table S-X). This indicates that relative efficacy of attractive LLINs decreases as the duration of the gonotrophic cycle increases and increases when the duration of the extrinsic incubation period increases (figure S-X). The model is also highly sensitive to the baseline daily survival rate (PIC = `r -round(pic["S",1],2)` [`r -round(pic["g",4],2)`, `r -round(pic["g",4],2)`]) and post-bite mortality in a hut equiped with an LLIN (PIC = `r -round(pic["m2p",1],2)` [`r -round(pic["m2p",4],2)`, `r -round(pic["m2p",5],2)`]). The model is slightly but significantly sensitive to  pre-bite mortality in a hut without LLIN (PIC = `r -round(pic["m1u",1],2)` [`r -round(pic["m1u",4],2)`, `r -round(pic["m1u",5],2)`]). 

```{r, echo=FALSE, fig.height = 4.5, fig.width = 6, fig.align = "center"}
figure_pse
pse::plotprcc(myLHS)
```





```{r echo=FALSE}
#### Supplementary Figure 1 plot preference value recorded by EHT in nature from two meta-analysis studies ----
# calculate prefernce value from field data
# from EHT in Moiroux et al. 2017, Plos One
Data_moiroux <- read.delim("data/Data_moiroux.txt")
Data_moiroux %>% 
	dplyr::filter(ITN == "no") %>% 
	select(Eval, total) %>% 
	right_join(Data_moiroux,by="Eval") %>% 
	#dplyr::filter(ITN == "ITN") %>%
	dplyr::filter(ITN != "no") %>%
	select(ttmt,total.x,total.y) %>%
	mutate(pLLIN = total.y/(total.y+total.x)) %>%
	mutate(study = "moiroux") %>%
	rename(Net = ttmt, TotalUTN = total.x, TotalITN = total.y) -> Data_pref_moiroux

# from EHT in Strode et al. 2014, Plos Med
Data_strode <- read.delim("data/Data_strode.txt")
Data_strode %>% 
	#filter(Intervention=="LLIN") %>%
	select(Net, TotalITN, TotalUTN) %>%
	mutate(study = "strode") %>%
	mutate(pLLIN = TotalITN / (TotalITN+TotalUTN)) -> Data_pref_strode

# bind the two dataframe together											 
Data_pref <- rbind(Data_pref_moiroux, Data_pref_strode)

# plot
supp_fig1 <- qplot( x=study , y=pLLIN , data=Data_pref , geom=c("boxplot","jitter") ,  ylab="Preference for treated net (pLLIN)")
supp_fig1

```

##### Supplementary Figure 1: Vector preference for insecticide treated nets measured in the fields through experimental hut trials.
###### *Data come from two studies [1,2]. Each point represent an ITN. There is 50 values coming from 9 EHT in the [1] data and 44 points coming from 13 EHT in the [2] data. Most values are below 0.5 indicating deterrence. About 25 % of the value are between 0.5 and 0.75 indicating attraction.*




```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
